From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-12-09 paper.tex
Updated template to IEEEtran

\documentclass{sig-alternate}

\usepackage{hyperref}

@@

@@

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{HRI}{'16 Chrischurch, New Zealand.}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}
\author{Séverin Lemaignan \qquad Fernando Garcia \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}

@@

%% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Experimentation, Human Factors.}

\keywords{Human-Robot Interaction; Social Robotics; Attention Assessment; Engagement; Computer Vision.}

@@

\bibliographystyle{abbrv}
\bibliography{sigproc}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}

\usepackage[utf8]{inputenc}
\usepackage{ gensymb } % for \degree
\usepackage{ amssymb } % for \varnothing

\usepackage{hyperref}
\usepackage{cite}

@@

\usepackage{amsmath}

@@

\begin{document}

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}

\author{\IEEEauthorblockN{Séverin Lemaignan, Fernando Garcia, Alexis Jacq, Pierre Dillenbourg}
\IEEEauthorblockA{
Computer-Human Interaction in Learning and Instruction Laboratory (CHILI) \\
École Polytechnique Fédérale de Lausanne (EPFL) \\
Lausanne, Switzerland \\
Email: \tt firstname.lastname@epfl.ch}
}

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{biblio}
\end{document}
